\title{Retrospective summary}
\date{\vspace{-5ex}}
\documentclass{article}
\usepackage[utf8]{inputenc}

\begin{document}
\maketitle
This sprint has been quite different for the team compared to the other ones. Overall, our workflow has been pretty much the same, if not identical to last sprint. So what went well previously has more or less gone the same course this time around. In fact, we completed most of our major key development with great margin due to our rutines we developed along the way. What is probably worth mentioning here this time around was what went bad, and that is the low motivation that hit the team towards the end of the project. Part of it was probably we had grown tired of the project, and the enthusiasm had faded away. Seeing the development coming to an end also gave many of us the mindset of being able to relax abit, and this quite hit the team's productivy at the end phase of the project. While this is quite a different aspect of "what went wrong", motivation to want to do this project is important as anything else. The best way to combat this would most likely to have ways to keep the team spirit up throughout the project. Looking back, planning poker would have been a good way to do this. While we made good use of it to make things more practical during development, we didn't really utilize the achievment aspect of it. Because we were late to corporate planning poker, we had little time to experiment with this. But we are pretty sure that if we had made us of it, it would have made a major difference.
\end{document}