\title{Retrospective summary}
\date{\vspace{-5ex}}
\documentclass{article}
\usepackage[utf8]{inputenc}

\begin{document}
\maketitle
Starting with what went well this time around, what really stood out was the possibility to get help from each other through Discord. The biggest reason for this is that every team member has been available on the chat pretty much alwas, meaning communication outside of the meetings has not been a problem at all. The team finds this communication to be gold, and do not want this to change.\\\\
Another thing that has worked very well is the Trello board. The Trello board has a complete overview of all tasks and problems. It acts as a TODO list and also as a log of everything that has been done. At the start we emphasized heavy on setting up the Trello board, which in turn gave us a well fleshed out task board. As the project went on, the team has been very diligent with adding tasks and problems that occurs, so the board was more or less always up to date with the current progress.\\\\
Going over what didn't work out as expected, number one thing was the identification of problems and tasks to be done, more specifically the size of the tasks. We took for granted the size of the tasks we distributed among each other. When we first distributed tasks amongst ourselve, we started with the pieces. This was a bad idea as we had not implemented or thought about the priority of what had to be done first, and most of us faced difficulties with implementing basic functions. Temporary solution to this was to implement enough of missing functionality in order to implement the pieces, but this was not ideal. We originally planned to do planning poker, but we totally forgot about it and just started coding right away. We also realized too late that the already distributed tasks could have been splitted into smaller tasks. This is something we have to remember for the next assignment and need to utilize planning poker to avoid such problems.\\\\
While the Trello board gave us a good overview of the project, the team was not diligent with tagging themselves on the cards and such. A few of us also started to make small changes here and there in other files which we had not tagged ourselves on. Both of these points resulted in changes that were not known, and albeit not big and fatal, merge conflicts happened. We want to be stricter with the tagging convention onwards to avoid these unecessary merge conflicts.\\\\
What we might want to try for the next assignmentis is to have the tasks as small as possible so that we can have daily progressnd to accomplish this task splitting, we will remember to use planning poker.

\end{document}